\documentclass[11pt]{article}
\usepackage{anysize}
\usepackage{graphicx}
\marginsize{1 in}{1 in}{0.5 in}{6 pt}
\title{Headmaster Dream Design}
\author{Chris Whiting}
%\setlength{\intextsep}{-0.5ex}
\begin{document}
\maketitle

 
\section{Top Level Design}
My idea for a dream headmaster interface starts with the headmaster login page. When the login page is opened in a browser, it will show the standard "Welcome to Headmaster" title, user id, and password. However, the login screen background will consist of an animated world, the expression "Welcome to Headmaster", and the normal login credential input fields.

As soon as the login button is pressed, the login credentials will fade away and the screen will zoom into a town consisting of a grassy area and one building, representing a school. The town also reads the value of the clock on your computer and outputs the cooresponding time of day where at night a moon would be out and the screen would be darker. Similar to the game Rollar Coaster Tycoon, little animated people will be walking around your town, which signify the students within headmaster. Each one is clickable, which brings up that particular students properties, which will be elaborated later on. At the top left of the page are options which read "Create Event", "Create Grant", "Create Report", and "Logout". Clicking on one of the three create buttons will bring to user to a separate field where a new building must be placed anywhere in the town. This new building is half the size of the school building, regardless of the type of building creation. That is, whether you make an event, grant, or report building, they will all be half the size of the school building. 

The event buildings will resemble a big tent, the grants buildings will resemble an office or government building, and the reports buildings will look like ordinary one story houses. Every one of these buildings will be the same color and style, however, their color may be changed. Once one of the smaller buildings is created, a menu similar to the menu from the old headmaster while creating events, grants, or reports. The name of each building is displayed over it and hovering your mouse over any of these buildings will make the name bigger, where these names coorespond to the name of the event, grant, or report. Double-clicking on any of these buildings will make the screen zoom into the entrance of the respective building and bring up a new view from the ceiling of the building. Many student avatars will be shown corresponding to the students related to that particular event, grant, or report. Students may be added to a building student properties section expanded upon later.

 of four big buildings, a space shuttle, a small building with a metal cog as its front store sign, and a lot of animated people walking around the town. This is similar to The Sims games where the virtual people are arbitrarily walking around. To expand, the first building looks like a school and has a giant S on the front of the building, representing students. The second building has a giant letter E as the front building sign, which represents events. The thrid building looks like a bank and has a big G at the front, standing for grants. The fourth big building, representing reports, has a R at the front of it. The small building with the metal cog represents the settings for the webpage, where the login page background can be slightly customized.

 The top of the webpage has a medium search bar, where the user may search for anything within headmaster, for example a student, events, grants, and/or reports. If the user is lazy and has no desire to use the keyboard, a voice command may also be issued by pressing a microphone icon next to the search bar. This feature is similar to Apple's Siri technology. 

An alternative, more satisfying way to search for students, grants, etc. is provided within this webpage as well. As a user mouses over any of the 6 items or buildings described above, they become illumniated and each respective building reveals its purpose. 

The S building cooresponds to the students tab on the headmaster webpage. When this building is clicked, my headmaster webpage will zoom in from the overall town view to into the building. Inside the S building consists of five doors which are again highlighted once the user puts his/her mouse over them. The doors consist of titles which are 'Freshman', 'Sophomores', 'Juniors', 'Seniors', and 'Create'. Similar to the town view above, a search bar is displayed at the top of the S building screen which allows the user to search for a individual student. Once the user enters any of the four doors, except the Create door, a view of a hallway with virutal people is displayed. The names of each person is displayed above their respective heads and the user may quickly go up and down the hallway via scrolling or the up and down arrow keys. The Create door brings the user to a similar view of editing a student, event, grant, etc., except the avatar is naked. He/she is clothed, however in very plain clothes, which can be customized during and after creation. All of the student's properties are displayed to the right of the avatar, as with the Edit button explained below, which start out as blank.

Once a student is pressed a separate screen with the selected student standing and slighting moving around, like the XBOX360 avatars, and a menu of student properties is displayed on the right. The student properties consist of Grades, Grants, Information, Food Allergies, etc and an Edit button. The Edit button may be pressed, which only changes the student properties page from non-editable to editable, while the avatar remains in the same place. Back arrows on the upper left of each screen within any of the S, H, G, etc. buildings will be displayed bringing the user back to the previous page. However, the user could always press the web browsers back button as well.

The S, E, G, and R buildings all have similar inside setups. The E building differs from the S building where instead of having students in the hallway, there are floating sports items, like basketballs. Which signify events and can be edited through the same method as the student edit operation described above. The G building holds floating scrolls instead of students, which represent grants. Clicking on a scroll will bring up a separate screen with the grant and its information. The building with the R contains floating paper and pencil icons representing the various reports in the headmaster system. 

Any person avatar in the headmaster system allows for basic customizations. The skin color, hair color, and clothing color can all be customized for each student within headmaster. This allows for variety during the homescreen where all of the avatars are onscreen walking around the virtual town.
%Things to ADD:
   1. Information about how to create new events, grants, and reports.
   2. Reorganize paragraphs so that it happens in chronological order.
   3. Add a picture of the xbox360 avatar creation screen and add it to the report.

\section{Usage Senarios}
The headmaster system is the beginning of a social networking website with many usage senarios. Two of the more common senarios would include creating a new student and creating an event.
\begin{enumerate}
    \item Scenario: Creating a new student
  \begin{enumerate}
        \item Login to headmaster
        \item Click on the S building
        \item Click on the Create Door
        \item Enter desired information and properties to new student.
        \item Save the new student with the save button.
  \end{enumerate}
    \item Scenario: Creating an event
  \begin{enumerate}
        \item Login to headmaster
        \item Click on the E building
        \item Click on the Create button
        \item Enter desired information and properties to new event.
        \item Save the new event with the save button.
  \end{enumerate}
\end{enumerate}

\section{Design Rationale}

\section{Usability Metric Analysis}
By far the strongest usability metric of my headmaster dream design is satisfaction. My design strives to give the user a pleasant experience while using headmaster. From the login screen the user is presented with a visually appealing view of the headmaster virtual world. When the user is navagating through different pages within headmaster, a zoom feature creates a more satisfying experience for the user. When double clicking a spot on Google maps and as the screen zooms in, a screen distortion occurs, which is similar to this headmaster feature.
The weakest metric is learnability, simply because the added satisfaction creates a better user experience, but makes the interface harder to learn. The time it takes for the user to learn an operation may be longer, because of the added satisfaction. When a user attempts to select a current headmaster student, the user must login, navigate to the S building and choose the particular student from the long row of them. However, a medium search bar is provided at the top to match the original headmaster. This helps learnability, because the user can recognize this similar element and already knows how to use it. However, the vastly different interface my dream design suggests is weak in learnability and strong in satisfaction.


\end{document}

